\documentclass[10pt]{article}
%\usepackage{fullpage}
\usepackage{color}
\usepackage{amssymb}
\title{\color{blue}\bf Math 308: Midterm 2}
\date{Wednesday, May 15, 2013}
\author{by William Stein}
\newcommand{\tf}[1]{\item {\bf {\color{blue}\hspace{1em}T\hspace{1em}F}}\hspace{1em} #1}
\begin{document}

\maketitle
{\noindent\bf\color{red} Instructions:}
\begin{itemize}
\item {\color{blue} Your Name: \underline{\hspace{20em}}\\ID Number: \underline{\hspace{10em}}}
\item You may have one piece of paper with notes, plus scratch paper.
\item You may use a calculator (but shouldn't need one).
\item Be careful.  Triple check your answer to every question.  Make sure you understand exactly what is being asked.
\item All questions are true or false and worth 5 points (for a total of 100 points).
\end{itemize}

{\noindent\bf \color{red} Questions (circle T or F):}
\begin{enumerate}

\tf{The function $f:\mathbb{R}^2\to \mathbb{R}^2$ given by $f(x,y) = (-2y,3x+1)$ is
a linear transformation.}

\tf{Suppose that a matrix $A$ has characteristic polynomial $f(x) = x \cdot (x^{2} - 15x - 18)$.  Then $A$ has exactly 2 distinct real eigenvalues.}

\tf{If $T:\mathbb{R}^2 \to \mathbb{R}^2$ is any linear transformation, then the
set of vectors $v$ such that $Tv=\left(\begin{array}{r}
0 \\
0
\end{array}\right)$ is a subspace of $\mathbb{R}^2$.}

\tf{There is a basis for $\mathbb{R}^2$ consisting of eigenvectors for $A=\left(\begin{array}{rrr}1 & 2013 \\0 & 1\end{array}\right)$.}

\tf{The characteristic polynomial of $A=\left(\begin{array}{rrr}
-1 & 0 & 2 \\
-1 & -3 & -1 \\
-3 & -1 & 1
\end{array}\right)$ is $$f(X)=(X - 3) \cdot (X^{2} + 4).$$}

\tf{Suppose $A$ and $B$ are $n\times n$ matrices with $|A|=5$ and $|B|=7$.
Then $$|A^2BA^{-1}B^{-1}A^{-1}| = 1.$$}

\tf{If $A$ is a symmetric matrix, then $|A|=1$.}

\tf{Suppose $A$ is an $n\times n$ matrix with $n\geq 1$.  If the equation $Ax=0$ has a unique solution, then $|A|=0$.}

\tf{The function $T:\mathbb{R}^2\to \mathbb{R}^5$ given by $f(x,y) = (x,x+y,x-y,0,y)$ is
a linear transformation.}

\tf{We have $|A|=112$, where $A=\left(\begin{array}{rrrrr}
1 & -4 & 2 & 1 & -2 \\
0 & -7 & 2 & 2 & 1 \\
0 & 0 & -2 & 7 & 1 \\
0 & 0 & 2 & 1 & 1 \\
0 & 0 & 0 & 0 & 1
\end{array}\right)$.}

\tf{We have $|A^{T}|=-112$, where $A$ is from the previous problem.}

\tf{Let $T$ be the linear transformation of $\mathbb{R}^2$ that rotates a vector by 90 degrees clockwise around the origin.  Then the matrix corresponding to $T$ is $\left(\begin{array}{rr}
0 & -1 \\
1 & 0
\end{array}\right)$.}

\tf{The matrix $A=\left(\begin{array}{rr}
1 & 2 \\
3 & 4
\end{array}\right)$ has no real eigenvalues.}

\tf{If $S$ and $T$ are both linear transformstions $\mathbb{R}^3\to \mathbb{R}^3$, then  $$f(v) = 2S(v) - 3T(v)$$ is necessarily also a linear transformation.}

\tf{If $A$ is an $n\times n$ matrix of integers, then the determinant of $A$ must necessarily also be an integer.}

\tf{If $A$ is any $n\times n$ matrix and $B$ is the reduced row echelon form of $A$, then  $|A|=|B|$.}

\tf{If $A$ is any $2\times 2$ matrix and $k$ any scalar, then $|kA| = k^4\cdot |A|$.}

\tf{If $v$ is an eigenvector with eigenvalue $\lambda$ of a matrix $A$, then
 $$A^{2013}v = \lambda^{2013} v.$$}

\tf{There are infinitely many linear transformations $T:\mathbb{R}^2\to \mathbb{R}^2$.}

\tf{Suppose $A$ is any invertible $2\times 2$ matrix with the two distinct eigenvalues $-1$ and $+1$.
Then we must have $A^2=I_2$, where $I_2$ is the $2\times 2$ identity matrix.}

\end{enumerate}

\end{document}